Reading main files and preparing data sets

### 2024-12-10 data-raw/03-preprocessing-main-files.Rmd
Socioeconomic variables from the 1992 GSS survey

```{r SURVMNTH}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # SURVMNTH: Survey month of data collection from April 2015 to March 2016
    SURVMNTH = 
           case_when(SURVMNTH == 1 ~ "January", 
                     SURVMNTH == 2 ~ "February",
                     SURVMNTH == 3 ~ "March",
                     SURVMNTH == 4 ~ "April",
                     SURVMNTH == 5 ~ "May",
                     SURVMNTH == 6  ~ "June",
                     SURVMNTH == 7 ~ "July",
                     SURVMNTH == 8 ~ "August",
                     SURVMNTH == 9 ~ "September",
                     SURVMNTH == 10 ~ "October",
                     SURVMNTH == 11 ~ "November",
                     SURVMNTH == 12 ~ "Devember",
                     SURVMNTH == 96 ~ "Valid skip",
                     SURVMNTH == 97 ~ "Don't know",
                     SURVMNTH == 98 ~ "Refusal",
                     SURVMNTH == 99 ~ "Not stated"), 
    SURVMNTH = factor(SURVMNTH))

@@

```{r SEX}
values_ordered <- c("Male", "Female")

@@

summary(gss_main_2010$SEXPR)
```
```{r PRTYPEC-2010}
gss_main_2010 <- gss_main_2010 %>% 
  mutate( # PRTYPEC: Type of partner respondent has living in the household.
    PRTYPEC = 
           case_when(PRTYPEC == 1 ~ "Opposite sex married partner in the household", 
                     PRTYPEC == 2 ~ "Opposite sex common-law partner in the household",
                     PRTYPEC == 3 ~ "Same sex married or common-law partner in the household",
                     PRTYPEC == 0 ~ "Respondent has no spouse/partner in the household "), 
    PRTYPEC = factor(PRTYPEC))

@@

summary(gss_main_2010$CHRFLAG)
```
```{r CHRINHSDC-2010}
values_ordered <- c("None", "One",
                     "Two",
                     "Three",
                     "Four or more children")

@@

gss_main_2010 <- gss_main_2010 %>% 
  mutate( # CHR0014C: Number of respondent's children living in the household (any age or marital status).
    CHR0014C = 
           case_when(CHR0014C == 0 ~ "None",
                     CHR0014C == 1 ~ "One",
                     CHR0014C == 2 ~ "Two",
                     CHR0014C == 3 ~ "Three or more children"), 
    CHR0014C = factor(CHR0014C, levels = values_ordered, ordered = TRUE)) 
summary(gss_main_2010$CHR0014C)
```
```{r CHRTIME6-2010}
gss_main_2010 <- gss_main_2010 %>% 
  mutate( # CHRTIME6:  Age group of respondent’s child(ren) in household
    CHRTIME6 = 
           case_when(CHRTIME6 == 1 ~ "No child under 19 years of age at home",
                     CHRTIME6 == 2 ~ "All children under 5 years of age",
                     CHRTIME6 == 3 ~ "All children between 5 and 12 years of age",
                     CHRTIME6 == 4 ~ "All children 13 years of age and older",
                     CHRTIME6 == 5 ~ "At least one child under 5 years of age but not all children",
                     CHRTIME6 == 6 ~ "Other"), 
    CHRTIME6 = factor(CHRTIME6))

summary(gss_main_2010$CHRTIME6)
```
```{r CHH0512C-2010}
values_ordered <- c("None", "One",
                     "Two",
                     "Three or more children")

gss_main_2010 <- gss_main_2010 %>% 
  mutate( # CHH0512C: Number of children aged from 5 to 12 years living in the respondent's household.
    CHH0512C = 
           case_when(CHH0512C == 0 ~ "None",
                     CHH0512C == 1 ~ "One",
                     CHH0512C == 2 ~ "Two",
                     CHH0512C == 3 ~ "Three or more children"), 
    CHH0512C = factor(CHH0512C, levels = values_ordered, ordered = TRUE)) 
summary(gss_main_2010$CHH0512C)
```
```{r CHH0014C-2010}
values_ordered <- c("None", "One",
                     "Two",
                     "Three or more children")

@@

@@

summary(gss_main_2005$CHRFLAG)
```
```{r CHRINHSDC-2005}
values_ordered <- c("None", "One",
                     "Two",
                     "Three",
                     "Four or more children")

@@

gss_main_2005 <- gss_main_2005 %>% 
  mutate( # CHR0014C: Number of respondent's children living in the household (any age or marital status).
    CHR0014C = 
           case_when(CHR0014C == 0 ~ "None",
                     CHR0014C == 1 ~ "One",
                     CHR0014C == 2 ~ "Two",
                     CHR0014C == 3 ~ "Three or more children"), 
    CHR0014C = factor(CHR0014C, levels = values_ordered, ordered = TRUE)) 
summary(gss_main_2005$CHR0014C)
```
```{r CHRTIME6-2005}
gss_main_2005 <- gss_main_2005 %>% 
  mutate( # CHRTIME6:  Age group of respondent’s child(ren) in household
    CHRTIME6 = 
           case_when(CHRTIME6 == 1 ~ "No child under 19 years of age at home",
                     CHRTIME6 == 2 ~ "All children under 5 years of age",
                     CHRTIME6 == 3 ~ "All children between 5 and 12 years of age",
                     CHRTIME6 == 4 ~ "All children 13 years of age and older",
                     CHRTIME6 == 5 ~ "At least one child under 5 years of age but not all children",
                     CHRTIME6 == 6 ~ "Other"), 
    CHRTIME6 = factor(CHRTIME6))

@@

summary(gss_main_2005$PRV) 
```
```{r REGION-2005}
gss_main_2005 <- gss_main_2005 %>% 
  mutate( # REGION:  Region of residence of the respondent.
    REGION = 
      case_when(REGION == 1 ~ "Atlantic region",
                     REGION == 2 ~ "Quebec",
                     REGION == 3 ~ "Ontario",
                     REGION == 4 ~ "Prairie region",
                     REGION == 5 ~ "British Columbia"),
    REGION = factor(REGION))

@@

summary(gss_main_2005$GTU_Q110)
```
```{r GTU_Q120-2005}
values_ordered <- c("More rushed",
                    "About the same",
                    "Less rushed",
                    "Don't know")

@@

>>>>

```{r SURVMNTH}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # SURVMNTH: Survey month of data collection from April 2015 to March 2016
    SURVMNTH = 
           case_when(SURVMNTH == 1 ~ "January", 
                     SURVMNTH == 2 ~ "February",
                     SURVMNTH == 3 ~ "March",
                     SURVMNTH == 4 ~ "April",
                     SURVMNTH == 5 ~ "May",
                     SURVMNTH == 6  ~ "June",
                     SURVMNTH == 7 ~ "July",
                     SURVMNTH == 8 ~ "August",
                     SURVMNTH == 9 ~ "September",
                     SURVMNTH == 10 ~ "October",
                     SURVMNTH == 11 ~ "November",
                     SURVMNTH == 12 ~ "December",
                     SURVMNTH == 96 ~ "Valid skip",
                     SURVMNTH == 97 ~ "Don't know",
                     SURVMNTH == 98 ~ "Refusal",
                     SURVMNTH == 99 ~ "Not stated"), 
    SURVMNTH = factor(SURVMNTH))

@@

```{r SEX-2015}
values_ordered <- c("Male", "Female")

@@

summary(gss_main_2010$SEXPR)
```

```{r PRTYPEC-2010}
gss_main_2010 <- gss_main_2010 %>% 
  mutate( # PRTYPEC: Type of partner respondent has living in the household.
    PRTYPEC = 
           case_when(PRTYPEC == 1 ~ "Opposite sex married partner in the household", 
                     PRTYPEC == 2 ~ "Opposite sex common-law partner in the household",
                     PRTYPEC == 3 ~ "Same sex married or common-law partner in the household",
                     PRTYPEC == 0 ~ "Respondent has no spouse/partner in the household "), 
    PRTYPEC = factor(PRTYPEC))

@@

summary(gss_main_2010$CHRFLAG)
```

```{r CHRINHSDC-2010}
values_ordered <- c("None", "One",
                     "Two",
                     "Three",
                     "Four or more children")

@@

gss_main_2010 <- gss_main_2010 %>% 
  mutate( # CHR0014C: Number of respondent's children living in the household (any age or marital status).
    CHR0014C = 
           case_when(CHR0014C == 0 ~ "None",
                     CHR0014C == 1 ~ "One",
                     CHR0014C == 2 ~ "Two",
                     CHR0014C == 3 ~ "Three or more children"), 
    CHR0014C = factor(CHR0014C, levels = values_ordered, ordered = TRUE)) 
summary(gss_main_2010$CHR0014C)
```

```{r CHRTIME6-2010}
gss_main_2010 <- gss_main_2010 %>% 
  mutate( # CHRTIME6:  Age group of respondent’s child(ren) in household
    CHRTIME6 = 
           case_when(CHRTIME6 == 1 ~ "No child under 19 years of age at home",
                     CHRTIME6 == 2 ~ "All children under 5 years of age",
                     CHRTIME6 == 3 ~ "All children between 5 and 12 years of age",
                     CHRTIME6 == 4 ~ "All children 13 years of age and older",
                     CHRTIME6 == 5 ~ "At least one child under 5 years of age but not all children",
                     CHRTIME6 == 6 ~ "Other"), 
    CHRTIME6 = factor(CHRTIME6))

summary(gss_main_2010$CHRTIME6)
```

```{r CHH0512C-2010}
values_ordered <- c("None", "One",
                     "Two",
                     "Three or more children")

gss_main_2010 <- gss_main_2010 %>% 
  mutate( # CHH0512C: Number of children aged from 5 to 12 years living in the respondent's household.
    CHH0512C = 
           case_when(CHH0512C == 0 ~ "None",
                     CHH0512C == 1 ~ "One",
                     CHH0512C == 2 ~ "Two",
                     CHH0512C == 3 ~ "Three or more children"), 
    CHH0512C = factor(CHH0512C, levels = values_ordered, ordered = TRUE)) 
summary(gss_main_2010$CHH0512C)
```

```{r CHH0014C-2010}
values_ordered <- c("None", "One",
                     "Two",
                     "Three or more children")

@@

```{r AGECHRYC-2005}

@@

summary(gss_main_2005$CHRFLAG)
```

```{r CHRINHSDC-2005}
values_ordered <- c("None", "One",
                     "Two",
                     "Three",
                     "Four or more children")

@@

gss_main_2005 <- gss_main_2005 %>% 
  mutate( # CHR0014C: Number of respondent's children living in the household (any age or marital status).
    CHR0014C = 
           case_when(CHR0014C == 0 ~ "None",
                     CHR0014C == 1 ~ "One",
                     CHR0014C == 2 ~ "Two",
                     CHR0014C == 3 ~ "Three or more children"), 
    CHR0014C = factor(CHR0014C, levels = values_ordered, ordered = TRUE)) 
summary(gss_main_2005$CHR0014C)
```

```{r CHRTIME6-2005}
gss_main_2005 <- gss_main_2005 %>% 
  mutate( # CHRTIME6:  Age group of respondent’s child(ren) in household
    CHRTIME6 = 
           case_when(CHRTIME6 == 1 ~ "No child under 19 years of age at home",
                     CHRTIME6 == 2 ~ "All children under 5 years of age",
                     CHRTIME6 == 3 ~ "All children between 5 and 12 years of age",
                     CHRTIME6 == 4 ~ "All children 13 years of age and older",
                     CHRTIME6 == 5 ~ "At least one child under 5 years of age but not all children",
                     CHRTIME6 == 6 ~ "Other"), 
    CHRTIME6 = factor(CHRTIME6))

@@

summary(gss_main_2005$PRV) 
```

```{r REGION-2005}
gss_main_2005 <- gss_main_2005 %>% 
  mutate( # REGION:  Region of residence of the respondent.
    REGION = 
      case_when(REGION == 1 ~ "Atlantic region",
                     REGION == 2 ~ "Quebec",
                     REGION == 3 ~ "Ontario",
                     REGION == 4 ~ "Prairie region",
                     REGION == 5 ~ "British Columbia"),
    REGION = factor(REGION))

@@

summary(gss_main_2005$GTU_Q110)
```

```{r GTU_Q120-2005}
values_ordered <- c("More rushed",
                    "About the same",
                    "Less rushed",
                    "Don't know")

@@

```{r reading-1998-main-file}
# Main File
gss_m_1998 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1998/gss-12M0012-E-1998-c-12-m_F1.csv"))
```

```{r filtering-variables-1998}
gss_main_1998 <- gss_m_1998 %>%
  select(RECID:DVTDAY)
```

```{r SURVMNTH-1998}
gss_main_1998 <- gss_main_1998 %>% 
  mutate( # SURVMNTH: Survey month of data collection from February 1998 to January 1999
    SURVMNTH = 
           case_when(SURVMNTH == 1 ~ "January", 
                     SURVMNTH == 2 ~ "February",
                     SURVMNTH == 3 ~ "March",
                     SURVMNTH == 4 ~ "April",
                     SURVMNTH == 5 ~ "May",
                     SURVMNTH == 6  ~ "June",
                     SURVMNTH == 7 ~ "July",
                     SURVMNTH == 8 ~ "August",
                     SURVMNTH == 9 ~ "September",
                     SURVMNTH == 10 ~ "October",
                     SURVMNTH == 11 ~ "November",
                     SURVMNTH == 12 ~ "December"), 
    SURVMNTH = factor(SURVMNTH))

summary(gss_main_1998$SURVMNTH)
```
```{r LANINT-1998}
gss_main_1998 <- gss_main_1998 %>% 
  mutate( # LANINT: Language of interview.
    LANINT = 
           case_when(LANINT == 1 ~ "English", 
                     LANINT == 2 ~ "French"), 
    LANINT = factor(LANINT))

summary(gss_main_1998$LANINT)
```
```{r AGEGR5-1998}
values_ordered <- c("15 to 17 years","18 to 19 years","20 to 24 years",
                    "25 to 29 years","30 to 34 years","35 to 39 year","40 to 44 years",
                    "45 to 49 years","50 to 54 years","55 to 59 year","60 to 64 years",
                    "65 to 69 years","70 to 74 years","75 to 79 year","80 years and over")

gss_main_1998 <- gss_main_1998 %>% 
  mutate( # AGEGR5: Age group of respondent (groups of 5)
    AGEGR5 = 
           case_when(AGEGR5 == 1 ~ "15 to 17 years",
                     AGEGR5 == 2 ~ "18 to 19 years",
                     AGEGR5 == 3 ~ "20 to 24 years",
                     AGEGR5 == 4 ~ "25 to 29 years",
                     AGEGR5 == 5 ~ "30 to 34 years",
                     AGEGR5 == 6  ~ "35 to 39 year",
                     AGEGR5 == 7 ~ "40 to 44 years",
                     AGEGR5 == 8 ~ "45 to 49 years",
                     AGEGR5 == 9 ~ "50 to 54 years",
                     AGEGR5 == 10 ~ "55 to 59 year",
                     AGEGR5 == 11 ~ "60 to 64 years",
                     AGEGR5 == 12 ~ "65 to 69 years",
                     AGEGR5 == 13 ~ "70 to 74 years",
                     AGEGR5 == 14 ~ "75 to 79 year",
                     AGEGR5 == 15 ~ "80 years and over"), 
    AGEGR5 = factor(AGEGR5, levels = values_ordered, ordered = TRUE))

summary(gss_main_1998$AGEGR5)
```

```{r AGEGR10-1998}
values_ordered <- c("15 to 24 years","25 to 34 years","35 to 44 years",
                    "45 to 54 years", "55 to 64 years","65 to 74 years","75 to 84 years", "85 years and over")

gss_main_1998 <- gss_main_1998 %>% 
  mutate( # AGEGR10: Age group of respondent (groups of 10)
    AGEGR10 = 
           case_when(AGEGR10 == 1 ~ "15 to 24 years", 
                     AGEGR10 == 2 ~ "25 to 34 years",
                     AGEGR10 == 3 ~ "35 to 44 years",
                     AGEGR10 == 4 ~ "45 to 54 years",
                     AGEGR10 == 5 ~ "55 to 64 years",
                     AGEGR10 == 6  ~ "65 to 74 years",
                     AGEGR10 == 7 ~ "75 to 84 years",
                     AGEGR10 == 8 ~ "85 years and over"), 
    AGEGR10 = factor(AGEGR10, levels = values_ordered, ordered = TRUE))

summary(gss_main_1998$AGEGR10)
```

```{r SEX-1998}
values_ordered <- c("Male", "Female")

gss_main_1998 <- gss_main_1998 %>% 
  mutate( # SEX: Sex of respondent
    SEX = 
           case_when(SEX == 1 ~ "Male", 
                     SEX == 2 ~ "Female"), 
    SEX = factor(SEX, levels = values_ordered, ordered = TRUE))

summary(gss_main_1998$SEX)
```

```{r MARSTAT}
gss_main_1998 <- gss_main_1998 %>% 
  mutate( # MARSTAT: Marital status of the respondent
    MARSTAT = 
           case_when(MARSTAT == 1 ~ "Married", 
                     MARSTAT == 2 ~ "Living common-law",
                     MARSTAT == 3 ~ "Widowed",
                     MARSTAT == 4 ~ "Separated",
                     MARSTAT == 5 ~ "Divorced",
                     MARSTAT == 6  ~ "Single, never married",
                     MARSTAT == 8 ~ "Don't know",
                     MARSTAT == 9 ~ "Not stated"), 
    MARSTAT = factor(MARSTAT))

summary(gss_main_1998$MARSTAT)
```

```{r AGEPRGR5-1998}
values_ordered <- c("Not Asked","15 to 19 years","20 to 24 years",
                    "25 to 29 years","30 to 34 years","35 to 39 year","40 to 44 years",
                    "45 to 49 years","50 to 54 years","55 to 59 year","60 to 64 years",
                    "65 to 69 years","70 to 74 years","75 to 79 year","80 years and over")

gss_main_1998 <- gss_main_1998 %>% 
  mutate( # AGEPRGR5: Age group of respondent (groups of 5)
    AGEPRGR5 = 
           case_when(AGEPRGR5 == 97 ~ "Not Asked",
                     AGEPRGR5 == 1 ~  "15 to 19 years",
                     AGEPRGR5 == 2 ~ "20 to 24 years",
                     AGEPRGR5 == 3 ~ "25 to 29 years",
                     AGEPRGR5 == 4 ~ "30 to 34 years",
                     AGEPRGR5 == 5  ~ "35 to 39 year",
                     AGEPRGR5 == 6 ~ "40 to 44 years",
                     AGEPRGR5 == 7 ~ "45 to 49 years",
                     AGEPRGR5 == 8 ~ "50 to 54 years",
                     AGEPRGR5 == 9 ~ "55 to 59 year",
                     AGEPRGR5 == 10 ~ "60 to 64 years",
                     AGEPRGR5 == 11 ~ "65 to 69 years",
                     AGEPRGR5 == 12 ~ "70 to 74 years",
                     AGEPRGR5 == 13 ~ "75 to 79 year",
                     AGEPRGR5 == 14 ~ "80 years and over"), 
    AGEPRGR5 = factor(AGEPRGR5, levels = values_ordered, ordered = TRUE))

summary(gss_main_1998$AGEPRGR5)
```
```{r PRTYPEC-1998}
gss_main_1998 <- gss_main_1998 %>% 
  mutate( # PRTYPEC: Type of partner respondent has living in the household.
    PRTYPEC = 
           case_when(PRTYPEC == 1 ~ "Respondent has a married partner in the household", 
                     PRTYPEC == 2 ~ "Respondent has a common-law partner in the household",
                     PRTYPEC == 0 ~ "Respondent has no spouse/partner in the household"), 
    PRTYPEC = factor(PRTYPEC))

summary(gss_main_1998$PRTYPEC)
```
```{r CHRFLAG-1998}
gss_main_1998 <- gss_main_1998 %>% 
  mutate( # CHRFLAG:  Child(ren) of the respondent living in the household.
    CHRFLAG = 
           case_when(CHRFLAG == 1 ~ "Yes", 
                     CHRFLAG == 2 ~ "No"), 
    CHRFLAG = factor(CHRFLAG))

summary(gss_main_1998$CHRFLAG)
```
```{r AGECHRYC-1998}

gss_main_1998 <- gss_main_1998 %>% 
  mutate( # AGECHRYC: Age of respondent's youngest child in household
           AGECHRYC = case_when(AGECHRYC == 25 ~ "25 and over",
                     AGECHRYC == 97 ~ "Not asked - no children in the household",
                     TRUE ~ as.character(AGECHRYC)), 
    AGECHRYC = factor(AGECHRYC, levels = values_ordered, ordered = TRUE))

summary(gss_main_1998$AGECHRYC)
```

```{r CHR0004C-1998}
values_ordered <- c("None", "One child",
                     "Two or more children")

gss_main_1998 <- gss_main_1998 %>% 
  mutate( # CHR0004C: Number of respondent’s children 0 to 4 years of age living in the household.
    CHR0004C = 
           case_when(CHR0004C == 0 ~ "None",
                     CHR0004C == 1 ~ "One child",
                     CHR0004C == 2 ~ "Two or more children"), 
    CHR0004C = factor(CHR0004C, levels = values_ordered, ordered = TRUE))

summary(gss_main_1998$CHR0004C)
```

```{r CHR0512C-1998}
values_ordered <- c("None", "One",
                     "Two",
                     "Three or more children")

gss_main_1998 <- gss_main_1998 %>% 
  mutate( # CHR0512C: Number of children aged from 5 to 12 years living in the respondent's household.
    CHR0512C = 
           case_when(CHR0512C == 0 ~ "None",
                     CHR0512C == 1 ~ "One",
                     CHR0512C == 2 ~ "Two",
                     CHR0512C == 3 ~ "Three or more children"), 
    CHR0512C = factor(CHR0512C, levels = values_ordered, ordered = TRUE)) 
summary(gss_main_1998$CHR0512C)
```

```{r CHR1314C-1998}
values_ordered <- c("None", "One child",
                     "Two or more children")

gss_main_1998 <- gss_main_1998 %>% 
  mutate( # CHR1314C: Number of respondent’s children 13 to 14 years of age living in the household.
    CHR1314C = 
           case_when(CHR1314C == 0 ~ "None",
                     CHR1314C == 1 ~ "One child",
                     CHR1314C == 2 ~ "Two or more children"), 
    CHR1314C = factor(CHR1314C, levels = values_ordered, ordered = TRUE))

summary(gss_main_1998$CHR1314C)
```

```{r CHR1518C-1998}
values_ordered <- c("None", "One child",
                     "Two or more children")

gss_main_1998 <- gss_main_1998 %>% 
  mutate( # CHR1518C: Number of respondent’s children 15 to 18 years of age living in the household.
    CHR1518C = 
           case_when(CHR1518C == 0 ~ "None",
                     CHR1518C == 1 ~ "One child",
                     CHR1518C == 2 ~ "Two or more children"), 
    CHR1518C = factor(CHR1518C, levels = values_ordered, ordered = TRUE))

summary(gss_main_1998$CHR1518C)
```

```{r CHR1924C-1998}
values_ordered <- c("None", "One child",
                     "Two or more children")

gss_main_1998 <- gss_main_1998 %>% 
  mutate( # CHR1924C: Number of respondent’s children 19 to 24 years of age living in the household.
    CHR1924C = 
           case_when(CHR1924C == 0 ~ "None",
                     CHR1924C == 1 ~ "One child",
                     CHR1924C == 2 ~ "Two or more children"), 
    CHR1924C = factor(CHR1924C, levels = values_ordered, ordered = TRUE))

summary(gss_main_1998$CHR1924C)
```
```{r CHR25UPC-1998}
values_ordered <- c("None", "One child",
                     "Two or more children")

gss_main_1998 <- gss_main_1998 %>% 
  mutate( # CHR25UPC: Number of respondent’s children 25 years of age and older living in the household.
    CHR25UPC = 
           case_when(CHR25UPC == 0 ~ "None",
                     CHR25UPC == 1 ~ "One child",
                     CHR25UPC == 2 ~ "Two or more children"), 
    CHR25UPC = factor(CHR25UPC, levels = values_ordered, ordered = TRUE))

summary(gss_main_1998$CHR25UPC)
```
```{r CHH0004C-1998}
values_ordered <- c("None", "One child",
                     "Two or more children")

gss_main_1998 <- gss_main_1998 %>% 
  mutate( # CHH0004C: Number of children aged from 0 to 4 living in the respondent’s household.
    CHH0004C = 
           case_when(CHH0004C == 0 ~ "None",
                     CHH0004C == 1 ~ "One child",
                     CHH0004C == 2 ~ "Two or more children"), 
    CHH0004C = factor(CHH0004C, levels = values_ordered, ordered = TRUE))

summary(gss_main_1998$CHH0004C)
```

```{r CHH1314C-1998}
values_ordered <- c("None", "One child",
                     "Two or more children")

gss_main_1998 <- gss_main_1998 %>% 
  mutate( # CHH1314C: Number of children aged from 13 to 14 living in the respondent’s household.
    CHH1314C = 
           case_when(CHH1314C == 0 ~ "None",
                     CHH1314C == 1 ~ "One child",
                     CHH1314C == 2 ~ "Two or more children"), 
    CHH1314C = factor(CHH1314C, levels = values_ordered, ordered = TRUE))

summary(gss_main_1998$CHH1314C)
```
```{r CHH0512C-1998}
values_ordered <- c("None", "One child",
                     "Two children","Three or more children")

gss_main_1998 <- gss_main_1998 %>% 
  mutate( # CHH0512C: Number of children aged from 13 to 14 living in the respondent’s household.
    CHH0512C = 
           case_when(CHH0512C == 0 ~ "None",
                     CHH0512C == 1 ~ "One child",
                     CHH0512C == 2 ~ "Two children",
                     CHH0512C == 3 ~ "Three or more children",), 
    CHH0512C = factor(CHH0512C, levels = values_ordered, ordered = TRUE))

summary(gss_main_1998$CHH0512C)
```

```{r CHRTIME6-2005}
gss_main_2005 <- gss_main_2005 %>% 
  mutate( # CHRTIME6:  Age group of respondent’s child(ren) in household
    CHRTIME6 = 
           case_when(CHRTIME6 == 1 ~ "No child under 19 years of age at home",
                     CHRTIME6 == 2 ~ "All children under 5 years of age",
                     CHRTIME6 == 3 ~ "All children between 5 and 12 years of age",
                     CHRTIME6 == 4 ~ "All children 13 years of age and older",
                     CHRTIME6 == 5 ~ "At least one child under 5 years of age but not all children",
                     CHRTIME6 == 6 ~ "Other"), 
    CHRTIME6 = factor(CHRTIME6))

```{r LIVARR08-1998}
gss_main_1998 <- gss_main_1998 %>% 
  mutate( # LIVARR08: Living arrangement of respondent’s household (8 categories)
    LIVARR08 = 
           case_when(LIVARR08 == 1 ~ "Under 25 years - Not living with parents",
                     LIVARR08 == 2 ~ "Under 25 years - Living with both parents",
                     LIVARR08 == 3 ~ "Under 25 years - Living with mother only",
                     LIVARR08 == 4 ~ "Under 25 years - Living with father only",
                     LIVARR08 == 5 ~ "25 years of age or older - Not living with parents",
                     LIVARR08 == 6 ~ "25 years of age or older - Living with both parents",
                     LIVARR08 == 7 ~ "25 years of age or older - Living with mother only",
                     LIVARR08 == 8 ~ "25 years of age or older - Living with father only"), 
    LIVARR08 = factor(LIVARR08))

summary(gss_main_1998$LIVARR08)
```

```{r LIVARR12-1998} 
gss_main_1998 <- gss_main_1998 %>% 
  mutate( # LIVARR12: Living arrangement of respondent’s household (12 categories)
    LIVARR12 = 
           case_when(LIVARR12 == 1 ~ "Living alone",
                     LIVARR12 == 2 ~ "Living with sponse only",
                     LIVARR12 == 3 ~ "Living with spouse and single child < 25 years",
                     LIVARR12 == 4 ~ "Living with spouse and single child 25 years or older",
                     LIVARR12 == 5 ~ "Living with spouse and non-child(ren)",
                     LIVARR12 == 6 ~ "Living with spouse and other",
                     LIVARR12 == 7 ~ "Living without spouse and single child  < 25 years",
                     LIVARR12 == 8 ~ "Living without spouse and single child 25 years or older",
                     LIVARR12 == 9 ~ "No spouse and non-single child(ren)",
                     LIVARR12 == 10 ~ "Living with two parents",
                     LIVARR12 == 11 ~ "Living with one parent",
                     LIVARR12 == 12 ~ "Other living arrangement"), 
    LIVARR12 = factor(LIVARR12))

summary(gss_main_1998$LIVARR12)
```

```{r HSDSIZEC-1998}
values_ordered <- c("One household member",
                   "Two household members",
                   "Three household members",
                   "Four household members",
                   "Five household members",
                   "Six household members",
                   "Seven household members", 
                   "Eight household members or more")

gss_main_1998 <- gss_main_1998 %>% 
  mutate( # HSDSIZEC: Household size of respondent
    HSDSIZEC = 
           case_when(HSDSIZEC == 1 ~ "One household member",
                     HSDSIZEC == 2 ~ "Two household members",
                     HSDSIZEC == 3 ~ "Three household members",
                     HSDSIZEC == 4 ~ "Four household members",
                     HSDSIZEC == 5 ~ "Five household members",
                     HSDSIZEC == 6 ~ "Six household members",
                     HSDSIZEC == 7 ~ "Seven household members",
                     HSDSIZEC == 8 ~ "Eight household members or more"), 
    HSDSIZEC = factor(HSDSIZEC, levels = values_ordered, ordered = TRUE))

summary(gss_main_1998$HSDSIZEC)
```

```{r FAMTYPE-1998}
gss_main_1998 <- gss_main_1998 %>% 
  mutate( # FAMTYPE: Respondent's type of family structure.
    FAMTYPE = 
           case_when(FAMTYPE == 1 ~ "Couple only", 
                     FAMTYPE == 2 ~ "Intact family",
                     FAMTYPE == 3 ~ "Step family with common child",
                     FAMTYPE == 4 ~ "Step family without a common child",
                     FAMTYPE == 5 ~ "Lone parent family",
                     FAMTYPE == 7 ~ "Not asked"), 
    FAMTYPE = factor(FAMTYPE))

summary(gss_main_1998$FAMTYPE)
```

```{r MULTIGEN-1998}
gss_main_1998 <- gss_main_1998 %>% 
  mutate( # MULTIGEN:  Three generations or more in the respondent’s household
    MULTIGEN = 
           case_when(MULTIGEN == 1 ~ "Yes", 
                     MULTIGEN == 2 ~ "No"), 
    MULTIGEN = factor(MULTIGEN))

summary(gss_main_1998$MULTIGEN)
```

```{r PRV-1998}
gss_main_1998 <- gss_main_1998 %>% 
  mutate( # PRV: Province of residence
    PRV = 
      case_when(PRV == 10 ~ "Newfoundland and Labrador",
                     PRV == 11 ~ "Prince Edward Island",
                     PRV == 12 ~ "Nova Scotia",
                     PRV == 13 ~ "New Brunswick",
                     PRV == 24 ~ "Quebec",
                     PRV == 35 ~ "Ontario",
                     PRV == 46 ~ "Manitoba",
                     PRV == 47 ~ "Saskatchewan",
                     PRV == 48 ~ "Alberta",
                     PRV == 59 ~ "British Columbia"),
    PRV = factor(PRV))

summary(gss_main_1998$PRV) 
```

```{r REGION-1998}
gss_main_1998 <- gss_main_1998 %>% 
  mutate( # REGION:  Region of residence of the respondent.
    REGION = 
      case_when(REGION == 1 ~ "Atlantic region",
                     REGION == 2 ~ "Quebec",
                     REGION == 3 ~ "Ontario",
                     REGION == 4 ~ "Prairie region",
                     REGION == 5 ~ "British Columbia"),
    REGION = factor(REGION))

summary(gss_main_1998$REGION)
```

```{r CMAPRV}
gss_main_1998 <- gss_main_1998 %>% 
  mutate( # CMAPRV:  Population centre indicator
    CMAPRV = 
      case_when(CMAPRV %in% c(6,8,11,13,15) ~ "CMA",
                     CMAPRV %in% c(1,2,3,4,5,7,9,10,12,14) ~ "non CMA"),
    CMAPRV = factor(CMAPRV))

summary(gss_main_1998$CMAPRV)
```

```{r A2-1998}
values_ordered <- c("Every day",
                    "A few times a week",
                    "About once a week",
                    "About once a month",
                    "Less than once a month",
                    "Never", 
                    "Not stated")

gss_main_1998 <- gss_main_1998 %>% 
  mutate( # A2: How often do you feel rushed?
    A2 = 
      case_when(A2 == 1 ~ "Every day",
                     A2 == 2 ~ "A few times a week",
                     A2 == 3 ~ "About once a week",
                     A2 == 4 ~ "About once a month",
                     A2 == 5 ~ "Less than once a month",
                     A2 == 6 ~ "Never",
                     A2 == 9 ~ "Not stated"),
    A2 = factor(A2, levels = rev(values_ordered), ordered = TRUE))

summary(gss_main_1998$A2)
```

```{r A3-1998}
values_ordered <- c("More rushed",
                    "About the same",
                    "Less rushed",
                    "Don't know","Not stated")

gss_main_1998 <- gss_main_1998 %>% 
  mutate( # A3: Compared to five years ago, do you feel...
    A3 = 
      case_when(A3 == 1 ~ "More rushed",
                     A3 == 2 ~  "About the same",
                     A3 == 3 ~ "Less rushed",
                     A3 == 8 ~ "Don't know",
                     A3 == 9 ~ "Not stated"),
    A3 = factor(A3, levels = rev(values_ordered), ordered = TRUE))

summary(gss_main_1998$A3)
```

```{r GTU_130-1998}
values_ordered <- c("Every day",
                    "A few times a week",
                    "About once a week",
                    "About once a month",
                    "Less than once a month",
                    "Never", 
                    "Not stated")

gss_main_1998 <- gss_main_1998 %>% 
  mutate( # A4: How often do you feel you have time on your hands that you don’t know what to do with?
    A4 = 
      case_when(A4 == 1 ~ "Every day",
                     A4 == 2 ~ "A few times a week",
                     A4 == 3 ~ "About once a week",
                     A4 == 4 ~ "About once a month",
                     A4 == 5 ~ "Less than once a month",
                     A4 == 6 ~ "Never",
                     A4 == 9 ~ "Not stated"),
    A4 = factor(A4, levels = rev(values_ordered), ordered = TRUE))

summary(gss_main_1998$A4)
```

```{r A5-1998}
gss_main_1998 <- gss_main_1998 %>% 
  mutate( # A5:  Do you feel that the days are just too short to do all the things you want?
    A5 = 
           case_when(A5 == 1 ~ "Yes", 
                     A5 == 2 ~ "No",
                     A5 == 9 ~ "Not stated", 
                     A5 == 8  ~ "Don't know"), 
    A5 = factor(A5))

summary(gss_main_1998$A5)
```

```{r A6-1998}
gss_main_1998 <- gss_main_1998 %>% 
  mutate( # A6: On which main activity would you choose to spend more time on
    A6 = 
      case_when(A6 == 1 ~ "Time with family and friends (spouse, children, boy-friend - girl-friend)",
                     A6 == 2 ~ "Relaxation - personal time",
                     A6 == 3 ~ "Practising sports",
                     A6 == 4 ~ "Crafts or hobbies",
                     A6 == 5 ~ "Outdoor activities",
                     A6 == 6 ~ "Reading - writing",
                     A6 == 7 ~ "Studies",
                     A6 == 8 ~ "Work",
                     A6 == 9 ~ "Domestic work",
                     A6 == 10 ~ "Holiday/Travel",
                     A6 == 11 ~ "Volunteer",
                     A6 == 12  ~ "Other",
                     A6 == 97  ~ "Not asked",
                     A6 == 98 ~ "Not stated",
                     A6 == 99 ~ "Don't know",
),
    A6 = factor(A6))
